\documentclass[11pt]{letter}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}

\begin{document}

\noindent
Aman Chandra H \& K.~C.~Narendra\\
School of Computer Science and Engineering\\
RV University, Bengaluru 560059, India\\
\href{mailto:amanch.btech23@rvu.edu.in}{amanch.btech23@rvu.edu.in}\\[1.5em]

\noindent \today\\[1.5em]

\noindent
Editor-in-Chief\\
\textit{IEEE Access}\\[1.5em]

\noindent Dear Editor-in-Chief,\\[0.8em]

We submit our manuscript, \textbf{``Severity-Weighted Calibration Error for Reliability Assessment Under Outcome-Severity Imbalance,''} for consideration as an Article in \textit{IEEE Access}.

\textbf{Problem.} Standard calibration metrics (e.g., ECE) are blind to subgroup failures. When high-risk cases are rare, models appear well-calibrated in aggregate while systematically underestimating risk for the most critical subgroups---precisely where miscalibration matters most.

\textbf{Contribution.} We propose \textbf{Severity-Weighted Calibration Error (SWCE)}, a post-hoc metric that incorporates outcome-severity weighting without model retraining. We demonstrate that aggregate metrics collapse to identical rankings when severe cases are rare ($<1\%$), proving that stratified evaluation is mathematically necessary, not merely preferable. We further provide a severity-stratified diagnostic framework and practical recalibration guidance.

\textbf{Suitability for IEEE Access.} The work addresses a fundamental limitation in probabilistic ML evaluation with broad applicability to any imbalanced prediction task---clinical, financial, or safety-critical---where rare high-stakes subgroups exist. All code is available at //
\href{https://github.com/amanchandrah895/swce-icu-calibration}{github.com/amanchandrah895/swce-icu-calibration}.

This manuscript is original, unpublished elsewhere, and approved by all authors. No conflicts of interest exist.

Thank you for your consideration.\\[1.5em]

\noindent Sincerely,\\[1em]

\noindent
Aman Chandra H\\
Corresponding Author\\[0.8em]

\noindent
K.~C.~Narendra

\end{document}